---
title: "R Notebook"
output: html_notebook
---

## Imputes most frequent missing locations values

Altogether, ~8,000 records out of ~139,000 missing records are imputed.

Reading data file created using munging1.Rmd (not munging2.Rmd)
```{r, echo=FALSE}
library(readr)
library(magrittr)
start <- Sys.time()
la_crimes <- read_csv("la_crimes.csv")
Sys.time() - start
```

Loading unmapped dataset created using munging2.Rmd
```{r}
unmapped_locations <- read_csv("unmapped_locations_2017_0216.csv")
```

Do a little manipulation of the coordinates column to get latitude and longtitude
```{r}
unmapped_locations$latitude <- sub(",.*", "", unmapped_locations$coordinates)
unmapped_locations$latitude <- as.numeric(unmapped_locations$latitude)
unmapped_locations$longitude <- sub(".* ", "", unmapped_locations$coordinates)
unmapped_locations$longitude <- as.numeric(unmapped_locations$longitude)
```

Do the imputation. This is the part that takes a LONG time due to the size of the files.
Takes about half an hour for 300 records.
```{r}
impute_lat <- function(this_location) {
  # Impute latitude
  # You have to use GLOBAL assignment: "<<-"!!
  # http://stackoverflow.com/questions/1236620/global-variables-in-r
  
  la_crimes[la_crimes$address == this_location & !is.na(la_crimes$address),]$latitude <<- unmapped_locations[unmapped_locations$address == this_location,]$latitude
}

impute_long <- function(a_location) {
  # Impute longitude
  # You have to use GLOBAL assignment: "<<-"!!
  # http://stackoverflow.com/questions/1236620/global-variables-in-r
  
  # Longitude to be imputed
  #imputed_long <- unmapped_locations[unmapped_locations$Incident_Location == a_location,]$longitude

  la_crimes[la_crimes$address == a_location & !is.na(la_crimes$address),]$longitude <<- unmapped_locations[unmapped_locations$address == a_location,]$longitude
}

start <- Sys.time()
# Suppress the output using invisible()
# http://stackoverflow.com/questions/2723034/suppress-one-commands-output-in-r
sapply(unmapped_locations$address[1:300], FUN = impute_lat) %>% invisible()
sapply(unmapped_locations$address[1:300], FUN = impute_long) %>% invisible()
Sys.time() - start
```

Write dataset with imputed values to file:
```{r}
write_csv(as.data.frame(la_crimes), "la_crimes_2017_0216.csv")
```